We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-05-08 paper/paper.tex
update

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
\caption{Asphericity scalars from observations as a function
  of satellite number. 
  Left: plane width; center: $c/a$ ratio;
  right: $b/a$ ratio. 
  These quantities can take positive or negative values because they
  were recentered to the mean and normalized to the standard deviation 
  of the spherically randomized satellites as explained in Section
  \ref{sec:normalization}. 
  The plane width and $c/a$ ratio for the MW is
  consistently found \emph{beyond} two standard
  deviations of the expected result for an statistically spherical
  distribution. 
  M31 shows the opposite trend and is always found
  \emph{within} two standard deviations. \label{fig:normalized_n}} 
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11.pdf}
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11.pdf}
\caption{Scalars in physical units describing satellite shape around the LG galaxies for
  a fixed number of satellites $N_s$=11: 
  plane width $w$, $c/a$ ratio and $b/a$ ratio.
  Left: M31, right: MW. 
  The histograms along the diagonal show the distribution for the
  $10^4$ values after spherical randomization; the vertical dashed
  lines show the 16, 50 and 84 percentiles of this distribution; the vertical solid line correspond to
  observations. 
  Outside the diagonal there are 2D histograms showing the $1$, $2$, $3$
  and $4\sigma$ contours for the randomized data.  
  The square at the center of the cross are observations.
  The blue circles are the results from Illustris-1-Dark. 
  For the M31 these three results
  (observations, randomized observations and simulations) seem to be
  in broad agreement, while for the MW they clearly differ. 
  The corresponding plots for Illustris-1 and ELVIS are
  in Figures \ref{fig:all_plots_illustris1} and
\ref{fig:all_plots_elvis}, respectively. \label{fig:physical_illustris1dark}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
\caption{Asphericity scalars from observations as a function
  of satellite number. 
  Left: plane width; center: $c/a$ ratio;
  right: $b/a$ ratio. 
  These quantities can take positive or negative values because they
  were recentered to the mean and normalized to the standard deviation 
  of the spherically randomized satellites as explained in Section
  \ref{sec:normalization}. 
  The plane width and $c/a$ ratio for the MW are
  consistently found \emph{beyond} two standard
  deviations of the expected result for an statistically spherical
  distribution. 
  M31 shows the opposite trend and are always found
  \emph{within} two standard deviations. \label{fig:normalized_n}} 
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11.pdf}
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11.pdf}
\caption{Scalars in physical units describing satellite shape around the LG galaxies for
  a fixed number of satellites $N_s$=11: 
  plane width $w$, $c/a$ ratio and $b/a$ ratio.
  Left: M31, right: MW. 
  The histograms along the diagonal show the distribution for the
  $10^4$ values after spherical randomization; the vertical dashed
  lines show the $16^{\rm th}$, $50^{\rm th}$ and $84^{\rm th}$
  percentiles of this distribution; the vertical solid line correspond
  to observations. 
  Outside the diagonal there are 2D histograms showing the ($1$, $2$,
  $3$) $\sigma$ contours for the randomized data.  
  The square at the center of the cross are observations.
  The blue circles are the results from Illustris-1-Dark. 
  For the M31 these three results
  (observations, randomized observations and simulations) seem to be
  in broad agreement, while for the MW they clearly differ. 
  The corresponding plots for Illustris-1 and ELVIS are
  in Figures \ref{fig:all_plots_illustris1} and
\ref{fig:all_plots_elvis}, respectively. \label{fig:physical_illustris1dark}}
\end{figure*}
